Procedural generation of levels fot he angry birds videogame using evolutionary computation\\

### 2019-05-14 IEEE_ConferenceOnGames/article_english.tex
Update to article 13/5/2019 23:14

\begin{itemize}
    \item Level Design: This aspect involves only the design of specific
    sections of a game, primarily those in which the player is able to interact.
    \item Audio: This aspect is focused on designing soundtracks that are able
    to react to a player specific action.
    \item Visuals: This area is focused on creating or improving visual
    representations of objects on games such as giving raw designs of players
    faces of improving the images of other graphics.
    \item Narrative: This aspect is focused on the generation of readable and
    coherent stories or plotlines of games.
    \item Gameplay: This aspect uses agents to test and evaluate the mechanic on
    which a game is based by trying to play as a human would in order to improve
    said mechanics.
    \item Game Design: This aspect is focused on generating the rulesets and mechanics of a new game. \cite{Yannakakis2017,Smith2014,shaker2016procedural}
\end{itemize}

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=90mm]{Images/ga_life_cycle.png}}
\caption{Life cycle of a genetic algorithm.}
\label{algorithm_model}
\end{figure}
% Maybe this is well known, again our implementation is what we need to describe 
% JJ, what you think?

@@

\section{Current approach}

In this Section we describe the approach that was used for this project, The
game contains a total of 11 pieces as shown on figure \ref{piece_list} that
cannot be modified, it is not possible to add more or modify the existing ones,
with this in mind the purpose is to create bundles of this same pieces in
different locations and angles in order to create structures that can be used as
building blocks for more complex levels, in order to do this a sequence of
events needs to be done as follows:

% Pleas explain in more detail this Composites in a section.

% Please use the name Composite instead of Bundle, composition is well known in
% object oriented design.

\begin{enumerate}
\item Generate the first generation of the population
\item Run a Simulation
\item Evaluate each member of the population
\item If a member of the population has remaining pieces obtain the location and
angle of the pieces, create a bundle and add it to the pool
\item Select the parents for the next generation
\item Do the crossover and mutation operations
\item Repeat the cycle
\end{enumerate}

@@

The rules for the competition specify that a configuration file must be used to
generate the levels of the game in a limited amount of time, the infornmation on
the configuration file is first the number of \textbf{\textit{diferent}} levels
that must be generated, the second value is the diferent materials \textit{not
allowed} to be used, for instance a group of generated levels must not have
circles which composition material is ice or stone moreover it des not have to
integrate a triangle piece with ice, stone or wood material so this combinations
must be removed from the pool of options, the third configuration value is the
\textit{number of pigs} that must be placed in a level, and finally the
\textit{limit} of time that the system has to create the required amount of
levels.

@@

additions to the piece pool are added to the population by the mutation
operation, the objective in the first phase of the project is to generate
structures that are capable of maintaining their own balance as shown on figure
\ref{test_old}, since the objective of open-ended evolution for this project is
to add new bundles to the pool of options the algorithm will first run a
simulation with a group of pieces and after it the ones that were not destroyed
by falling because of gravity will be saved and added to the pool of options.

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=80mm]{Images/simulation_bef_aft_example.png}}
\caption{Structure at beginning and end of a simulation.}
\label{test_old}
\end{figure}
% Here it's explained better, maybe this paragraph should be moved to
% an earlier point - MG

% Needs a few touches - MG
In order to add a bundle of pieces as a new component first it has to be
measured, an imaginary bounding box is defined by calculating the lengths of all
the pieces, finding the borders of said pieces and find the points that could
define a box around all of them, calculate the height and width then calculate
the center point of said box and calculate the offsets from the center of the
group to the center of each respective piece as shown on figure
\ref{bounding_boc_calc}, this information is needed in order to add it as a new
element so it can be used to place the pieces in their respective new positions
when the files needed for the simulation are being created.

@@

\section{Future work}

>>>>

\begin{itemize}
    \item Level Design: This aspect involves only the design of specific
    sections of a game, primarily those in which the player is able to interact.
    \item Audio: This aspect is focused on designing soundtracks that are able
    to react to a player specific action.
    \item Visuals: This area is focused on creating or improving visual
    representations of objects on games such as giving raw designs of players
    faces of improving the images of other graphics.
    \item Narrative: This aspect is focused on the generation of readable and
    coherent stories or plotlines of games.
    \item Gameplay: This aspect uses agents to test and evaluate the mechanic on
    which a game is based by trying to play as a human would in order to improve
    said mechanics.
    \item Game Design: This aspect is focused on generating the rulesets and 
    mechanics of a new game. \cite{Yannakakis2017,Smith2014,shaker2016procedural}
    % The references are in this last item of the list JS
\end{itemize}

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=90mm]{Images/ga_life_cycle.png}}
\caption{Life cycle of a genetic algorithm.}
\label{algorithm_model}
\end{figure}

% Maybe this is well known, again our implementation is what we need to describe 
% JJ, what you think?

@@

\section{Approach}

In this Section we describe the first approach that was used for this project, the
game contains a total of 11 pieces as shown on figure \ref{piece_list} that
cannot be modified, it is not possible to add more or modify the existing ones,
with this in mind the purpose is to create composites of this same pieces in
different locations and angles in order to create structures that can be used as
building blocks for more complex levels.

Since there is no way to \textit{add} a composite to the pool of pieces of the 
game then a way to combine both groups is needed, in order to do this first the 
original 11 pieces of the game will be converted into composites, since the easiest
way to read the data to create composites is by using lists then a \textit{composite} 
of one element will be created for each piece, after this in order to add a 
composite of pieces as a new component first a group of existing composites is 
selected and placed in a imaginary enviroment then as a unique group they are 
measured, an imaginary bounding box is defined by calculating the lengths of all
the pieces, finding the borders of said pieces and then find the points that could
define a box around all of them, then use this defined box to calculate the 
height and width of the new composite and then calculate from 
the center point of said box the offsets from the center of the
group to the center of each respective piece as shown on figure
\ref{bounding_boc_calc}, this information is needed in order to add it as a new
composite so it can be used to place the pieces in their respective new positions
when the files needed for the simulation are being created.

So using the composite generator the order of this sequence of
events needs to be done as follows:

% Pleas explain in more detail this Composites in a section.  
% Here it's explained better, maybe this paragraph should be moved to
% an earlier point - MG

% Needs a few touches - MG
% Please use the name Composite instead of Bundle, composition is well known in
% object oriented design.

\begin{enumerate}
\item Gnerate composited to add to the pool of options
\item Generate the first generation of the population
\item Run a Simulation
\item Evaluate each member of the population
\item If a member of the population has remaining pieces obtain the location and
angle of the pieces, create a composite and add it to the pool
\item Select the parents for the next generation
\item Do the crossover and mutation operations
\item Repeat the cycle
\end{enumerate}

@@

The Angry Birds level generation track is a competition where the objective is 
to generate levels that are \textit{fun} and \textit{enjoyable} however they 
also have to be challenging but imposible however the rules for the competition 
specify that a configuration file must be used to
generate the levels of the game in a limited amount of time, the infornmation on
the configuration file is first the number of \textbf{\textit{diferent}} levels
that must be generated, the second value is the diferent materials \textit{not
allowed} to be used, for instance a group of generated levels must not have
circles which composition material is ice or stone moreover it des not have to
integrate a triangle piece with ice, stone or wood material so this combinations
must be removed from the pool of options, the third configuration value is the
\textit{number of pigs} that must be placed in a level, and finally the
\textit{limit} of time that the system has to create the required amount of
levels.

@@

additions to the piece pool are added to the population by the mutation
operation, the objective in the first phase of the project is to generate
structures that are capable of maintaining their own balance as shown on figure
\ref{test_old}, since the objective of open-ended evolution for this project is
to add new composites to the pool of options the algorithm will first run a
simulation with a group of pieces and after it the ones that were not destroyed
by falling because of gravity will be saved and added to the pool of options.

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=80mm]{Images/simulation_bef_aft_example.png}}
\caption{Structure at beginning and end of a simulation.}
\label{test_old}
\end{figure}

@@

\section{Conclusions and future work}
